Palaeodistribution of crop progenitors and wild foods in the Southern Levant

### 2023-08-03 analysis/analysis.Rmd
Update TODOs

```{r model}
# TODO: Investigate where these NAs are coming from
rand_forest(mode = "regression") |>
  fit(as.numeric(present) ~ ., data = select(occ, present, starts_with("bio_"))) ->
  rf_fit
```

@@

```{r predict}
# TODO: deal with missing data in pred vars
# TODO: turn back to something spatial? stars?
predict(rf_fit, climate$cur)
```

>>>>

```{r model}
# TODO: Deal with missing values
rand_forest(mode = "regression") |>
  fit(as.numeric(present) ~ ., data = select(occ, present, starts_with("bio_"))) ->
  rf_fit
```

@@

```{r predict}
predict(rf_fit, climate$cur)
```
